One of the main methodological limitations we encountered in this study was the fact that we could not use Android devices to collect survey data, so our data collection was limited to iPhones only. This limitation has a significant impact on the generalizability of our results, as Android has a significant share of the global smartphone market. The exclusion of Android devices may lead to a skewed understanding of cross-device tracking behaviors and patterns, potentially overlooking findings relevant to the Android ecosystem. Furthermore, we were not able to intercept HTTP requests from within an application, which would also have been interesting additional data to investigate

In terms of technical and operational challenges, the main challenge we faced was that a significant amount of cross-device tracking activity takes place on the server side, beyond the reach of traditional data collection tools. This server-side operation was a big challenge for us, as it limits insight into the mechanisms and decision-making processes that drive cross-device tracking. Server-side tracking involves data processing and linking that is not directly observable, making it difficult to assess the full scope and effectiveness of advertisers' and platforms' cross-device tracking strategies.

Our study primarily focused on deterministic cross-device tracking methods that link devices based on identifiable information, such as login credentials. While deterministic tracking is a reliable means of establishing connections between devices, it is only one part of the cross-device tracking landscape. Probabilistic tracking methods, which infer device connections based on behavioral patterns and device characteristics, remain largely unexplored in our research due to their complexity and the impossibility of proving them. This focus on deterministic methods limits our understanding of the cross-device identification and tracking techniques described in Part 1.

In conclusion, while this study contributes valuable insights into cross-device tracking practices, it is also limited by various factors. Future research should aim to address these limitations by incorporating a broader array of devices, exploring probabilistic tracking methods, and developing techniques to shed light on server-side tracking operations.